Joint maximum-likelihood of phylogeny and ancestral states is not consistent

### 2018-10-04 joint_inf.tex
em-dash looked too much like a minus

In words, the joint estimation procedure does not recover the true generating $t^*$ almost everywhere in the space of generating parameters.
%EM Totally confused here!
%EM 1. The generating probabilities do contain x* and y*.
%EM 2. "This is apparent" makes it sound like it should follow directly and that it doesn't require a proof.
%das: ok, took a stab at clarifying
For example, in estimating $x_1$, $\hat{x}_1$ is a linear combination of $p_{\siteSplit_j}$ values.
For the generating probabilities (top panel of Table~\ref{tab:gen-sitepatprob}), there is no linear combination that results in an isolated $x^*$ term, as all terms are either quadratic---$(x^*)^2$ and $(x^*)^2(y^*)^2$---or have both $x^*$ and $y^*$---$x^*(y^*)^2$.
Thus, we cannot obtain a linear combination that in the general case yields $x^*$.
We may have special cases where certain $x^*$ and $y^*$ values yield consistent estimates for $\hat{t}$, but consistency does not hold in general.
We give an example of consistency in a degenerate case in the Appendix following the proof of Theorem~\ref{thm:bl_theorem}.

>>>>

In words, the joint estimation procedure does not recover the true generating $t^*$ almost everywhere in the space of generating parameters.
%EM Totally confused here!
%EM 1. The generating probabilities do contain x* and y*.
%EM 2. "This is apparent" makes it sound like it should follow directly and that it doesn't require a proof.
%das: ok, took a stab at clarifying
For example, in estimating $x_1$, $\hat{x}_1$ is a linear combination of $p_{\siteSplit_j}$ values.
For the generating probabilities (top panel of Table~\ref{tab:gen-sitepatprob}), there is no linear combination that results in an isolated $x^*$ term, as all terms are either quadratic, i.e., $(x^*)^2$ or $(x^*)^2(y^*)^2$, or have both $x^*$ and $y^*$, i.e., $x^*(y^*)^2$.
Thus, we cannot obtain a linear combination that in the general case yields $x^*$.
We may have special cases where certain $x^*$ and $y^*$ values yield consistent estimates for $\hat{t}$, but consistency does not hold in general.
We give an example of consistency in a degenerate case in the Appendix following the proof of Theorem~\ref{thm:bl_theorem}.
